Offshore Blue Crab Densities for <br/> The Gulf of Mexico

### 2020-01-28 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
model updates

The following numbers are from the Western Gulf Dataset used in the generalized linear model*

```{r}
start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
overall_foa <- mean(seamap_west$crab_presence, na.rm = TRUE) * 100
overall_mean <- mean(seamap_west$cpue_towspd, na.rm = T)
percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap_west %>% count()
```

@@

 * Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`

 * Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%

@@

*NOTE: Zeros removed for plotting*

@@

@@

@@

>>>>

**The following numbers are from all usable data from 2000-2018**

```{r seamap all stats}
start_year <- min(as.numeric(as.character(seamap$survey_year)))
end_year <- max(as.numeric(as.character(seamap$survey_year)))
total_catch <- sum(seamap$sapidus_catch, na.rm = T)
overall_foa <- mean(seamap$crab_presence, na.rm = TRUE) * 100
overall_mean <- mean(seamap$cpue_towspd, na.rm = T)
percent_zeros <- seamap %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap %>% count()

#seamap %>% group_by(survey_year) %>% summarise(foa = mean(crab_presence)) %>% arrange(foa)

 * Overall Mean Catch Crabs/Hectare: `r overall_mean`

 * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%

**The following numbers are from the Western Gulf Dataset used in the generalized linear model**

```{r seamap west stats}
start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
overall_foa <- mean(seamap_west$crab_presence, na.rm = TRUE) * 100
overall_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap_west %>% count()

@@

 * Overall Mean Catch Crabs/Hectare: `r overall_mean`

 * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%

@@

@@

**Model Selection using AIC**

@@

**Predictor Significance using Chi-Square LRT and Deviance**

#broom::glance(best_mod) %>% kable()
#Percent deviance explained
perc_dev <- (best_mod$null.deviance - best_mod$deviance) / best_mod$null.deviance
perc_dev <- round(perc_dev * 100,2)
```

*Percent Deviance Explained by Best Candidate Model:* `r perc_dev`

@@

#Estimated Marginal Means with an offset
#parameter in the call of offset = 0:
best_mod_dat <- as.data.frame(emmeans(best_mod, 
                                  specs = "year_f", 
                                  by    = c("region", "season"),
                                  type  = "response", 
                                  offset = 0))
best_mod_dat$CV <- best_mod_dat$SE/best_mod_dat$response

#Drop Infinite credibility intervals
best_mod_dat <- best_mod_dat %>% 
  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL))

# #Observed data
# mean_obs <- mean(seamap_west$cpue_towspd)
# obs_timeline <- seamap_west %>% 
#   group_by(survey_year, region, season) %>% 
#   summarise(Nobs = n(),
#             PercentPos = mean(crab_presence),
#             Mean_CPUE = mean(cpue_towspd)) %>% 
#   mutate(Index_Obs = Mean_CPUE/mean_obs)

#ggplot of standardized index of abundance
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
      #Fitted Data
      geom_line(aes(year_n, response, color = season)) +
      geom_point(aes(year_n, response, color = season, shape = season)) +
      # Observed Data
      # geom_line(data = obs_timeline, 
      #         aes(survey_year, Mean_CPUE, group = region), 
      #         col = "royalblue", linetype = 2) +
      # geom_point(data = obs_timeline, 
      #            aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
      scale_color_grey(start = 0.2, end = 0.6) + 
      labs(
        x = NULL, 
        y = "Crabs per Hectare",
        title = "Model Estimates and Yearly observed means") +
      facet_grid(region ~ .) +
  theme(
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank())
p
